
\documentclass{article}
\begin{document}

\title{Problem Set 5}
\author{Zavala}
\date{}
\maketitle

\section*{Web Scraping: MLB 2024 Standings}

For this problem set, I scraped data from Baseball Reference 
(https://www.baseball-reference.com/leagues/majors/2024-standings.shtml), 
which contains the 2024 MLB team standings. The data includes each team's 
wins, losses, win-loss percentage, and games behind the division leader.

This data interests me because baseball statistics are a classic example 
of structured, publicly available sports data. It could be useful in the 
future for analyzing team performance trends, building predictive models 
for playoff outcomes, or comparing team performance across seasons.

I did not use any online tutorials to scrape this data. I used the 
\texttt{rvest} package in R along with the \texttt{html\_nodes()} and 
\texttt{html\_table()} functions to extract the standings table directly 
from the webpage.

\end{document}


\section*{API Data: MLB 2024 Home Run Leaders}

For this section, I used the MLB Stats API (statsapi.mlb.com) to retrieve 
the 2024 MLB home run leaders. The API is free and requires no API key, 
making it very accessible. I pulled the top 20 home run leaders for the 
2024 season.

The data shows Aaron Judge of the New York Yankees leading with 58 home runs, 
followed by Shohei Ohtani of the Los Angeles Dodgers with 54. It is 
interesting to see how dominant these two players were compared to the rest 
of the league.

This data could be useful for analyzing power hitting trends across teams 
and leagues. I used the \texttt{rjson} package in R to call the API and 
parse the JSON response into a data frame.

\end{document}
